PineAPPL:\\ combining EW and QCD corrections for PDF fits

### 2020-08-17 paper/app-addmaterial.tex
section 3
Fix a few grammatical/typographical mistakes

In this appendix, we collect some additional plots, in the same format of those
presented in figures~\ref{fig:atlaszhighmass49fb}--\ref{fig:cmsZ13TeV},
specifically: figure~\ref{fig:atlaszhighmass49fb-lowstat} is the same as
figure~\ref{fig:atlaszhighmass49fb}, but for a low-statistic MC run;
figure~\ref{fig:cmsdy2d11_bins12} is the same as
figure~\ref{fig:cmsdy2d11_bins3456}, but for the two missing lepton-pair
invariant mass bins,
$\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{30}{\giga\electronvolt}$ and
$\SI{30}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{45}{\giga\electronvolt}$;
and figure~\ref{fig:atlastop-rap} is the same as figure~\ref{fig:atlastop},
but for the distributions in the rapidity of the top quark, $y_{\mathrm{t}}$,
and in the rapidity of the top-quark pair, $y_{\mathrm{t}\bar{\mathrm{t}}}$. In this
case the factorisation and renormalisation scales are kept equal to
$H_T/s$, see section~\ref{sec:toppair}.

>>>>

In this appendix we collect some additional plots, in the same format of those
presented in figures~\ref{fig:atlaszhighmass49fb}--\ref{fig:cmsZ13TeV},
specifically: figure~\ref{fig:atlaszhighmass49fb-lowstat} is the same as
figure~\ref{fig:atlaszhighmass49fb}, but for a low-statistic MC run;
figure~\ref{fig:cmsdy2d11_bins12} is the same as
figure~\ref{fig:cmsdy2d11_bins3456}, but for the two missing lepton-pair
invariant mass bins,
$\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{30}{\giga\electronvolt}$ and
$\SI{30}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{45}{\giga\electronvolt}$;
and figure~\ref{fig:atlastop-rap} is the same as figure~\ref{fig:atlastop},
but for the distributions in the rapidity of the top quark, $y_{\mathrm{t}}$,
and in the rapidity of the top-quark pair, $y_{\mathrm{t}\bar{\mathrm{t}}}$. In this
case the factorisation and renormalisation scales are kept equal to
$H_\mathrm{T}/4$, see section~\ref{sec:toppair}.

### 2020-08-17 paper/app-lumis.tex
Fix a few grammatical/typographical mistakes

%-------------------------------------------------------------------------------
\begin{table}[!t]
  \centering
  \tiny
  \input{tables/TableB1.tex}\\
  \caption{The 35 parton luminosities contributing to the predictions, accurate
    to NLO QCD+EW, of the Drell--Yan lepton-pair production measured by the
    ATLAS experiment at a centre-of-mass energy of
    \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}. The contributions
    are reported, in percentage, for each of the thirteen bins. The bin edges
    are in the invariant mass of the lepton pair, $M_{\ell\bar\ell}$, as follows:
    116, 130, 150, 170, 190,
    210, 230, 250, 300, 400, 500, 700, 1000, 1500 GeV.}
  \label{tab:B1}
\end{table}
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
\begin{table}[!p]
  \centering
  \tiny
  \input{tables/TableB2.tex}\\
  \caption{The 35 parton luminosities contributing to the predictions, accurate
    to NLO QCD+EW, of the double differential Drell--Yan lepton pair production
    measured by the CMS experiment at a centre-of-mass energy of
    \SI{7}{\tera\electronvolt}~\cite{Chatrchyan:2013tia}. The invariant mass
    bin is $\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{30}{\giga\electronvolt}$; bins 1-24 are in the rapidity of the lepton pair,
  $0.0<y_{\ell\bar\ell}<2.4$, and each bin has a width of 0.1.}
  \label{tab:B2}
\end{table}
%-------------------------------------------------------------------------------

@@

%-------------------------------------------------------------------------------
\begin{table}[!p]
  \centering
  \tiny
  \input{tables/TableB8.tex}\\
  \input{tables/TableB9.tex}\\
  \caption{The 37 parton luminosities contributing to the predictions,
    accurate to NLO QCD+EW, to the top-quark pair distributions measured by the
    ATLAS and CMS experiments at a centre-of-mass-energy of
    $\SI{8}{\tera\electronvolt}$~\cite{Aad:2015mbv,Khachatryan:2015oqa}.
    From left to right, top to bottom,
    predictions are reported for the 8 bins of transverse momentum of the
    top quark, for the 5 bins of top-quark rapidity, for the 7 bins of
    top-quark pair invariant mass, and for the 5 bins of top-quark pair
  rapidity, see text for details.}
  \label{tab:B8}
\end{table}
%-------------------------------------------------------------------------------

@@

In this appendix, we present the complete breakdown of parton luminosities
entering the NLO QCD+EW predictions of the various measurements
considered in section~\ref{sec:results}. For each parton luminosity,
we indicate its percentage contribution to the cross section in a given bin.
In particular:
\begin{itemize}
\item Table~\ref{tab:B1} collects the thirty-five parton luminosities
  contributing to the Drell--Yan lepton-pair production measured by the
  ATLAS experiment at a centre-of-mass energy of
  \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}.
  The thirteen bins are for the invariant mass of the lepton pair,
  $M_{\ell\bar\ell}$, with edges at 116, 130, 150, 170, 190,
  210, 230, 250, 300, 400, 500, 700, 1000 and 1500 GeV.
\item Tables~\ref{tab:B2}--\ref{tab:B7} collect the thirty-five parton
  luminosities contributing to the double differential Drell--Yan lepton-pair
  production measured by the CMS experiment at a centre-of-mass energy of
  \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}. The one hundred and thirty-two
  bins are split across tables~\ref{tab:B2}--\ref{tab:B7}, where each table
  corresponds to a bin in the invariant mass of the lepton pair:
  table~\ref{tab:B2} to  $\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{30}{\giga\electronvolt}$; table~\ref{tab:B3} to  $\SI{30}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{45}{\giga\electronvolt}$; table~\ref{tab:B4} to  $\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$; table~\ref{tab:B5} to  $\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$; table~\ref{tab:B6} to $\SI{120}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{200}{\giga\electronvolt}$; and table~\ref{tab:B7} to $\SI{120}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$. In each table, the bins are in the rapidity of the lepton pair, $0.0<y_{\ell\bar\ell}<2.4$, and each of them has a width of 0.1 (0.2 in the largest invariant mass range).
\item Table~\ref{tab:B8} collects the thirty-seven parton luminosities
  contributing to the top-quark pair distributions measured by the ATLAS and
  CMS experiments at a centre-of-mass energy of
  \SI{8}{\tera\electronvolt}~\cite{Aad:2015mbv,Khachatryan:2015oqa}.
  The four distributions, differential in the transverse momentum of the top
  quark, $p_\mathrm{T}^\mathrm{t}$, in the rapidity of the top quark,
  $y_\mathrm{t}$, in the invariant mass of the top-quark pair,
  $m_{\mathrm{t}\bar{\mathrm{t}}}$, and in the rapidity of the top-quark pair,
  $y_{\mathrm{t}\bar{\mathrm{t}}}$ are shown. The bin edges are, respectively:
  0, 60, 100, 150, 200, 260, 320, 400, 500~GeV; 0.0, 0.4, 0.8, 1.2, 1.6, 2.5;
  345, 400, 470, 550, 650, 800, 1100, 1600~GeV;
  and 0.0, 0.3, 0.6, 0.9, 1.3, 2.5.
\item Table~\ref{tab:B10} collects the one hundred and sixty-six
  parton luminosities contributing to the Z $p_{\mathrm{T}}$ distribution
  measured by the CMS experiment at a centre-of-mass energy of
  \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}. The bin edges are:
  20, 22, 26, 28, 32, 37, 43, 52, 65, 85, 120, 160, 190, 220, 250, 300,
  400, 500, 800, 1500~GeV.
\end{itemize}

>>>>

%-------------------------------------------------------------------------------
\begin{table}[!t]
  \centering
  \tiny
  \input{tables/TableB1.tex}\\
  \caption{The 35 parton luminosities contributing to the predictions, accurate
    to NLO QCD+EW, of the Drell--Yan lepton-pair production measured by the
    ATLAS experiment at a centre-of-mass energy of
    \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}. The contributions
    are reported, in percentage, for each of the 13 bins. The bin edges
    are in the invariant mass of the lepton pair, $M_{\ell\bar\ell}$, as follows:
    116, 130, 150, 170, 190,
    210, 230, 250, 300, 400, 500, 700, 1000, 1500 GeV.}
  \label{tab:B1}
\end{table}
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
\begin{table}[!p]
  \centering
  \tiny
  \input{tables/TableB2.tex}\\
  \caption{The 35 parton luminosities contributing to the predictions, accurate
    to NLO QCD+EW, of the double differential Drell--Yan lepton pair production
    measured by the CMS experiment at a centre-of-mass energy of
    \SI{7}{\tera\electronvolt}~\cite{Chatrchyan:2013tia}. The invariant mass
    bin is $\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{30}{\giga\electronvolt}$; bins 1--24 are in the rapidity of the lepton pair,
  $0.0<y_{\ell\bar\ell}<2.4$, and each bin has a width of 0.1.}
  \label{tab:B2}
\end{table}
%-------------------------------------------------------------------------------

@@

%-------------------------------------------------------------------------------
\begin{table}[!p]
  \centering
  \tiny
  \input{tables/TableB8.tex}\\
  \input{tables/TableB9.tex}\\
  \caption{The 37 parton luminosities contributing to the predictions,
    accurate to NLO QCD+EW, to the top-quark pair distributions measured by the
    ATLAS and CMS experiments at a centre-of-mass-energy of
    $\SI{8}{\tera\electronvolt}$~\cite{Aad:2015mbv,Khachatryan:2015oqa}.
    From left to right, top to bottom,
    predictions are reported for the eight bins of transverse momentum of the
    top quark, for the five bins of top-quark rapidity, for the seven bins of
    top-quark pair invariant mass, and for the five bins of top-quark pair
  rapidity, see text for details.}
  \label{tab:B8}
\end{table}
%-------------------------------------------------------------------------------

@@

In this appendix, we present the complete breakdown of parton luminosities
entering the NLO QCD+EW predictions of the various measurements
considered in section~\ref{sec:results}. For each parton luminosity,
we indicate its percentage contribution to the cross section in a given bin.
In particular:
\begin{itemize}
\item Table~\ref{tab:B1} collects the 35 parton luminosities
  contributing to the Drell--Yan lepton-pair production measured by the
  ATLAS experiment at a centre-of-mass energy of
  \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}.
  The 13 bins are for the invariant mass of the lepton pair,
  $M_{\ell\bar\ell}$, with edges at 116, 130, 150, 170, 190,
  210, 230, 250, 300, 400, 500, 700, 1000 and 1500 GeV.
\item Tables~\ref{tab:B2}--\ref{tab:B7} collect the 35 parton
  luminosities contributing to the double differential Drell--Yan lepton-pair
  production measured by the CMS experiment at a centre-of-mass energy of
  \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}. The 132
  bins are split across tables~\ref{tab:B2}--\ref{tab:B7}, where each table
  corresponds to a bin in the invariant mass of the lepton pair:
  table~\ref{tab:B2} to  $\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{30}{\giga\electronvolt}$; table~\ref{tab:B3} to  $\SI{30}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{45}{\giga\electronvolt}$; table~\ref{tab:B4} to  $\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$; table~\ref{tab:B5} to  $\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$; table~\ref{tab:B6} to $\SI{120}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{200}{\giga\electronvolt}$; and table~\ref{tab:B7} to $\SI{120}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$. In each table, the bins are in the rapidity of the lepton pair, $0.0<y_{\ell\bar\ell}<2.4$, and each of them has a width of 0.1 (0.2 in the largest invariant mass range).
\item Table~\ref{tab:B8} collects the 37 parton luminosities
  contributing to the top-quark pair distributions measured by the ATLAS and
  CMS experiments at a centre-of-mass energy of
  \SI{8}{\tera\electronvolt}~\cite{Aad:2015mbv,Khachatryan:2015oqa}.
  The four distributions, differential in the transverse momentum of the top
  quark, $p_\mathrm{T}^\mathrm{t}$, in the rapidity of the top quark,
  $y_\mathrm{t}$, in the invariant mass of the top-quark pair,
  $m_{\mathrm{t}\bar{\mathrm{t}}}$, and in the rapidity of the top-quark pair,
  $y_{\mathrm{t}\bar{\mathrm{t}}}$ are shown. The bin edges are, respectively:
  0, 60, 100, 150, 200, 260, 320, 400, 500~GeV; 0.0, 0.4, 0.8, 1.2, 1.6, 2.5;
  345, 400, 470, 550, 650, 800, 1100, 1600~GeV;
  and 0.0, 0.3, 0.6, 0.9, 1.3, 2.5.
\item Table~\ref{tab:B10} collects the 166
  parton luminosities contributing to the Z $p_{\mathrm{T}}$ distribution
  measured by the CMS experiment at a centre-of-mass energy of
  \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}. The bin edges are:
  20, 22, 26, 28, 32, 37, 43, 52, 65, 85, 120, 160, 190, 220, 250, 300,
  400, 500, 800, 1500~GeV.
\end{itemize}
